\part{Text}

\section{Polishing the plain text}
\begin{frame}
	\tableofcontents[currentsection,hideothersubsections]
\end{frame}

\subsection{UTF-8 encoding}

\begin{frame}[fragile]
	\frametitle{Use UTF-8 encoding in \LaTeX}
	UTF-8 encoding is widely used in modern computer applications, so it's useful to include the \structure{inputenc} package and use UTF-8 encoding.
	\begin{command}
		\mintinline{latex}{\usepackage[utf-8]{inputenc}}
	\end{command}
	\begin{example}
		café
	\end{example}
	However, different operating systems and compiling engines have different support on UTF-8 encoding, some UTF-8 codes that work on your computer may not work on others (though rarely), so it is recommended to use commands (will be introduced later) instead of directly copy and paste the UTF-8 codes from the Internet.
\end{frame}

\subsection{Special symbols and accents}

\begin{frame}
	\frametitle{Special symbols}
	Some special symbols can't be directly used since they are reserved by \LaTeX
	\begin{center}
	\begin{tabular}{llllll}
		\samplesymbol{\#}{\#} & \samplesymbol{\$}{\$} & \samplesymbol{\%}{\%} & \samplesymbol{\&}{\&} & \samplesymbol{\~{}}{\~{}} & \samplesymbol{\`{}}{\`{}} \\
		\samplesymbol{\{}{\{} & \samplesymbol{\}}{\}} & \samplesymbol{\_}{\_} &
		\multicolumn{2}{l}{\samplesymbol{textbackslash}{\textbackslash}}
	\end{tabular}
	\end{center}
	Many \LaTeX\ starters are confused with how to correctly print quotes, hyphens and dots.\\
	\`{} prints a left single quote, ' prints a right single quote.\\
	\`{}\`{} prints a left double quote, '' prints a right double quote.\\
	one hyphen (-) print like - \\
	two hyphens ({-}{-}) print like -- \\
	three hyphens ({-}{-}{-}) print like ---\\
	\samplecommand{dots} prints the dots with a correct format (\dots) instead of directly use three dots (...)
\end{frame}

\begin{frame}
	\frametitle{Accent on letters}
	Sometimes you may need an accent form of a letter, here is an example of letter \structure{o}
	\begin{center}
	\begin{tabular}{lllll}
		\sampleaccent{\`{}}{\`}{o} & \sampleaccent{'}{\'}{o} & \sampleaccent{\^{}}{\^}{o} & \sampleaccent{"}{\"}{o} & \sampleaccent{\~{}}{\~}{o} \\
		\sampleaccent{=}{\=}{o} & \sampleaccent{.}{\.}{o} & \sampleaccent{u}{\u}{o} & \sampleaccent{v}{\v}{o} & \sampleaccent{H}{\H}{o}\\
		\sampleaccent{t}{\t}{oo} & \sampleaccent{r}{\r}{o} & \sampleaccent{c}{\c}{o} & \sampleaccent{d}{\d}{o} & \sampleaccent{b}{\b}{o}
	\end{tabular}
	\end{center}
	\begin{block}{Something interesting}
		You may be curious about how to print words like \LaTeX, actually it's defined as a command.
		\begin{itemize}
			\item \samplecommand{TeX} - \TeX
			\item \samplecommand{LaTeX} - \LaTeX
			\item \samplecommand{LaTeXe} - \LaTeXe
		\end{itemize}
	\end{block}
\end{frame}

\subsection{Fonts}

\begin{frame}
	\frametitle{Basic commands about fonts}
	First, lets start with some commands that transform font types
	\begin{itemize}
		\item \sampletext{bf}{\bf}
		\item \sampletext{it}{\it}
		\item \sampletext{rm}{\rm}
		\item \sampletext{sc}{\sc}
		\item \sampletext{sf}{\sf}
		\item \sampletext{sl}{\sl}
		\item \sampletext{tt}{\tt}
	\end{itemize}
	Note that the commands that transform font types influence the text in the whole scope (\structure{\{...\}}) until another font type is specified. For example, how to use the first command \samplecommand{bf} is shown below\\[0.5em]
	\{\samplecommand{bf} Sample Text\}
\end{frame}

\begin{frame}[fragile]
	Sometimes we don't want to transform  all the font types, instead, we can only change the font type of some specified text.
	\begin{example}
		\begin{minted}{latex}
\textbf{Sample text}
		\end{minted}
	\end{example}
	There are more options for fonts.
	\begin{itemize}
		\item \sampletext{textit}{\textit}
		\item \sampletext{textsc}{\textsc}
	\end{itemize}
	However, in a math environment (will be introduced later), some other commands should be used
	\begin{itemize}
		\item \samplecommand{mathbf} - $\mathbf{Sample\ Text}$
		\item \samplecommand{mathit} - $\mathit{Sample\ Text}$
		\item \samplecommand{mathsf} - $\mathsf{Sample\ Text}$
	\end{itemize}
	Note that the math environment doesn't include all of the font types on the previous page. More information about font types can be found \href{http://www.cnblogs.com/make217/p/6123532.html}{\color{blue}\underline{here}}.
\end{frame}

\begin{frame}
	Font size can also be easily modified
	\begin{itemize}
		\item \sampletext{tiny}{\tiny}
		\item \sampletext{scriptsize}{\scriptsize}
		\item \sampletext{footnotesize}{\footnotesize}
		\item \sampletext{small}{\small}
		\item \sampletext{normalsize}{\normalsize}
		\item \sampletext{large}{\large}
		\item \sampletext{Large}{\Large}
		\item \sampletext{LARGE}{\LARGE}
		\item \sampletext{huge}{\huge}
		\item \sampletext{Huge}{\Huge}
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Build a colorful document}
	Changing the color is similar to changing font types.\\[0.5em]
	If you want to transform to a color (like \samplecommand{bf}), you can use \samplecommand{color}\{\structure{name}\}\\
	Similarly, you can use \samplecommand{textcolor}\{\structure{name}\} like \samplecommand{textbf}\\
	The background color of the whole page can be set using \samplecommand{pagecolor}\{\structure{name}\}\\[0.5em]
	There are some defined color \structure{name} in the \structure{xcolor} package.\\[0.5em]
	\begin{tabular}{lllll}
	\samplecolorbox{black}&\samplecolorbox{gray}&\samplecolorbox{olive}&\samplecolorbox{teal}&\samplecolorbox{blue}\\
	\samplecolorbox{green}&\samplecolorbox{orange}&\samplecolorbox{violet}&\samplecolorbox{brown}&\samplecolorbox{lightgray}\\
	\samplecolorbox{pink}&\samplecolorbox{white}&\samplecolorbox{cyan}&\samplecolorbox{lime}&\samplecolorbox{purple}\\
	\samplecolorbox{yellow}&\samplecolorbox{darkgray}&\samplecolorbox{magenta}&\samplecolorbox{red}\\
	\end{tabular}
	\\[0.5em]
	You can find more information in the documentation of \structure{xcolor} (\alert{texdoc} \structure{xcolor})
\end{frame}

\subsection{Underline}

\begin{frame}
	\frametitle{Ulem package}
	If you want to add some lines on the text, use the \structure{ulem} package.
	\begin{command}
		\samplecommand{usepackage}\{ulem\}\\
		\samplecommand{uline}\{Sample Text\}
	\end{command}
	There are different kinds of lines supported:
	\begin{itemize}
		\item \sampletext{uline}{\uline}
		\item \sampletext{uuline}{\uuline}
		\item \sampletext{uwave}{\uwave}
		\item \sampletext{sout}{\sout}
		\item \sampletext{xout}{\xout}
		\item \sampletext{dashuline}{\dashuline}
		\item \sampletext{dotuline}{\dotuline}
	\end{itemize}
\end{frame}

\section{Typesetting}
\begin{frame}
	\tableofcontents[currentsection,hideothersubsections]
\end{frame}

\subsection{Enumeration}
\begin{frame}[fragile]
	\frametitle{Enumerate}
	When you need to enumerate some items as a list, you may use the \structure{enumerate} package.
	\begin{command}
		\begin{minted}{latex}
\usepackage{enumerate}
\begin{enumerate}[style]
\item % ...
\item % ...
\item % ...
\end{enumerate}
		\end{minted}
	\end{command}
	This will generate a normal list with the serial numbers in the specified \structure{style}, which could be the following (as example)
	\begin{itemize}
		\item \alert{1} - 1, 2, 3, 4, ...
		\item \alert{(i)} - (i), (ii), (iii), (iv), ...
		\item \alert{[1.]} - [1.], [2.], [3.], [4.], ...
	\end{itemize}
\end{frame}

\begin{frame}[fragile]
	\frametitle{Itemize}
	If you want to generate an unordered list, use \structure{itemize} instead of \structure{enumerate}.
	\begin{command}
		\begin{minted}{latex}
\usepackage{enumerate}
\begin{itemize}
\item[style] % ...
\item[style] % ...
\item[style] % ...
\end{itemize}
		\end{minted}
	\end{command}
	In this case, \structure{style} must be added after each item, which is different from that in \structure{enumerate}, and the symbol displayed in the beginning of each item will be exactly same as the \structure{style}. If \structure{style} is not added, a default style will be used.
\end{frame}

\subsection{Alignment}

\begin{frame}[fragile]
	\frametitle{Alignment}
	If you want to align a paragraph of text, use these three environments for left/center/right align.
	\begin{command}
		\samplebegin{flushleft/center/flushright}\\
		\qquad ...\\
		\sampleend{flushleft/center/flushright}
	\end{command}
	However, if only a single line needs to be aligned, use these three commands.
	\begin{command}
		\begin{minted}{latex}
\leftline{}
\centerline{}
\rightline{}
		\end{minted}
	\end{command}
\end{frame}

\subsection{Spaces, lines and pages}

\begin{frame}
	\frametitle{Spaces may be confusing}
	There are defined command of spaces in different width and usages.
	\begin{itemize}
		\item \colorbox{yellow}{\ } - the basic space in \LaTeX\ (printed in yellow since it's transparent). Note that any number of spaces or tabs is equal to one space, and the space after a command is ignored. If you want to add an extra space, use \alert{\textbackslash}\colorbox{yellow}{\ } which makes a 1/3\,em space (1 em is approximately the width of an \structure{M} in the current font)
		\item \~{} - If two words can't be separated on two lines, you can tell \LaTeX\ about it using a tie (\~{}), such as Prof.\~{}Hamade (Prof.~Hamade).
		\item  \samplecommand{,} - makes a 1/6\,em space, commonly used before units (notice the space before em on this page)
		\item  \samplecommand{;} - makes a 2/7\,em space
		\item  \samplecommand{quad} - makes a 1\,em space
		\item  \samplecommand{qquad} - makes a 2\,em space
		\item  \samplecommand{phantom}\{\structure{text}\} - makes actually the space of \structure{text}, but \structure{text} will be invisible.
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Separate contents into lines and pages}
	Here are some basic commands about lines and pages in \LaTeX, you will use them everywhere.
	\begin{itemize}
		\item \samplecommand{newline} - begin a new line
		\item \alert{\textbackslash\textbackslash} - begin a new line
		\item \samplecommand{par} - begin a new paragraph(a new line with indent)
		\item \alert{\textbackslash\textbackslash [}\structure{offset}\alert{]} - begin a new line with an vertical offset, \structure{offset} is the size of needed space
		\item \samplecommand{linebreak} - begin a new line with the words discrete
		\item \samplecommand{newpage} - begin a new page
		\item \alert{\%} - begin a line comment
	\end{itemize}
\end{frame}

\begin{frame}[fragile]
	\frametitle{Precise Spacing/Unprecise Spacing}
	When trying to separate two paragraphs by a certain space, many new learners of \LaTeX\ may use multiple empty lines and linebreaks, which is not so accurate. Actually, \LaTeX\ provides a precise spacing mechanism.
	\begin{command}
		\mintinline{latex}{\vspace{space}}\\
		\mintinline{latex}{\vspace*{space}}
	\end{command}
	When trying to show the next paragraph or sentence precisely at the bottom of the current page, we can use
	\begin{command}
		\mintinline{latex}{\vfill}
	\end{command}
	between the contents of two paragraphs to separate them.
\end{frame}

\begin{frame}
	\frametitle{Spacing units}
	The \structure{space} can be anything representing a size, such as \structure{1cm}, \structure{2em} and \structure{10pt}. In \LaTeX, spacing units can be
	\begin{itemize}
		\item \structure{cm}
		\item \structure{mm}
		\item \structure{in} - inch, 1 inch = 2.54 cm
		\item \structure{pt} - 72 pt = 1 inch, the smallest unit in \LaTeX
		\item \structure{em} - 1em equals to the width of letter M
		\item \structure{ex} - 1ex equals to the width of letter x
		\item \samplecommand{linewidth} - the width of current line in the container
		\item \samplecommand{pagewidth} - the width of the page
		\item \samplecommand{pageheight} - the height of the page
		\item \samplecommand{textwidth} - the normal width of text on the page
		\item \samplecommand{textheight} - the normal height of text on the page
	\end{itemize}
\end{frame}

\subsection{Minipage and Multicolumn}

\begin{frame}[fragile]
	\frametitle{Minipage}
	\structure{minipage} is a very useful environment for dividing pages into a grid.
	\begin{example}
		\begin{multicols}{2}
			\inputminted[xleftmargin=1.5em]{latex}{examples/minipage.tex}
		\end{multicols}
	\end{example}
\end{frame}

\begin{frame}
	The code above generate six minipages in a grid of 3 columns $\times$ 2 rows. Don't try to add up the width of minipages in a line for more than about \LC{0.98\linewidth} (since a minipage have a small margin on each side), or the last minipage may be on a new line. \\[0.5em]
	For each minipage, it can be seem as an independent \LaTeX\ document, where text, formulas, graphics, tables and etc. can be inserted, and most importantly, they won't affect each other. What's more, you can even use minipages in a minipage to form a multi-level nesting. \\
\end{frame}

\begin{frame}[fragile]
	\frametitle{The multicol package}
	When typesetting contents with small line width and many lines (for example, source code), the \structure{multicol} package is recommended.
	\begin{command}
		\begin{minted}{latex}
\usepackage{multicol}
\begin{multicols}{cols}
    % contents on column one
    \breakcolumn % break the current column here
    % contents on column two
\end{multicols}
		\end{minted}
	\end{command}
	Here \structure{cols} is the number of columns, it must be specified. If \LC{\breakcolumn} is not used, the \structure{multicol} package will automatically balance the length of each column.
\end{frame}

\section{Learn more - multi languages and scope in \LaTeX}
\begin{frame}
	\tableofcontents[currentsection,hideothersubsections]
\end{frame}

\subsection{Multiple Languages}

\begin{frame}[fragile]
	\frametitle{Spelling languages}
	If you want to use a spelling language with characters similar to English, package \structure{babel} can be used (exactly the same name as \href{http://babeljs.io/}{babel}).
	\begin{command}
		\mintinline{latex}{\usepackage[languages]{babel}}
		\footnotesize
		\begin{itemize}
			\item \structure{languages} - a list of languages, the last one to be the default language
		\end{itemize}
	\end{command}
	\begin{example}
		\mintinline{latex}{\usepackage[greek,english]{babel}} \\
		\mintinline{latex}{\textgreek{abcdefgABCDEFG}}
	\end{example}
	Then \LaTeX\ will print \textgreek{abcdefgABCDEFG} \\
	Of course, you can use some simple commands to print these greek letters directly, such as \LC{\alpha}, \LC{\beta} and etc, which is more convenient only when few of them are needed.
\end{frame}

\begin{frame}[fragile]
	\frametitle{Chinese}
	The Chinese TeX Community maintains a package called \structure{ctex} for inputing Chinese in \LaTeX. Note that it is only a package, which is shipped with most modern \TeX\ Suites, not the \structure{CTEX} Suite. I don't think it's a good choice to use the \structure{CTEX} Suite directly.
	\begin{command}
		\mintinline{latex}{\usepackage{ctex}}
	\end{command}
	The default \LaTeX\ compiler \structure{pdflatex} doesn't have support on Chinese input with \structure{ctex} package, \structure{xelatex} is a recommended modern \LaTeX\ compiler as a replacement. \\

	However, the \structure{ctex} package is too heavy and it can slow down the total compilation speed seriously. 
\end{frame}

\subsection{Scope}

\begin{frame}[fragile]
	\frametitle{Usage of scope in \LaTeX}
	First, you should realize the meaning of ``scope'' in programming. Let's start with a simple example in C/C++ (assuming you know that):
	\inputminted{c++}{examples/scope.cpp}
\end{frame}

\begin{frame}[fragile]
	In the example of C/C++, we use brackets \structure{\{\}} to define a scope, which is just the same in \LaTeX. In addition, notice that an environment or a command also defines a scope.

	\begin{example}
	\begin{multicols}{2}
		\inputminted{latex}{examples/scope.tex}
		\columnbreak
		\input{examples/scope.tex}
	\end{multicols}
	\end{example}

	With the usage of scopes, you can flexibly change the color, font or anything else you wish in a self-defined range of the document.

\end{frame}
